Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-13 output/latex/manuscript.tex
add funding in acknowledgements

>>>>

This work was supported by grants from the Gordon and Betty Moore Foundation (GBMF 4552), the National Human Genome Research Institute (R01 HG010067), the National Cancer Institute (R01 CA237170), and The Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765) to CSG; and the National Human Genome Research Institute (K99HG011898 and 4R00HG011898) to MP.
